The Array of Long-Baseline Antennas for Taking Radio Observations from the Sub-Antarctic

### 2020-05-13 albatros_paper.tex
added plot of synthesized beam

Using the eight coastal huts, the \prizm\ site, and the hydro shack as
the nominal \albatros\ installation locations, the computed
synthesized beam is as shown in \autoref{Fig:marion}.  The beam width
at 5~MHz is roughly \SI{8}{\arcminute}, which represents over an order
of magnitude improvement in resolution over other existing
measurements.  One of the challenges in constructing an interferometer
array on Marion Island is that the rugged terrain precludes the
possibility of directly cabling and correlating antennas across large
distances.  The final \albatros\ antenna stations will therefore
operate {\it autonomously}, recording baseband data over extended
periods of time for subsequent offline correlation.  We have conducted
two enginering runs: 1) a two-element, directly correlated pathfinder
to qualitatively understand the sky signal, and 2) a single station to
test the readout and power handling technology that are required for
autonomous operation.

>>>>

Using the eight coastal huts, the \prizm\ site, and the hydro shack as
the nominal \albatros\ installation locations, the computed
synthesized beam is as shown in \autoref{Fig:beam}.  The beam width
at 5~MHz is roughly \SI{8}{\arcminute}, which represents over an order
of magnitude improvement in resolution over other existing
measurements.  One of the challenges in constructing an interferometer
array on Marion Island is that the rugged terrain precludes the
possibility of directly cabling and correlating antennas across large
distances.  The final \albatros\ antenna stations will therefore
operate {\it autonomously}, recording baseband data over extended
periods of time for subsequent offline correlation.  We have conducted
two enginering runs: 1) a two-element, directly correlated pathfinder
to qualitatively understand the sky signal, and 2) a single station to
test the readout and power handling technology that are required for
autonomous operation.

\begin{figure}
  \begin{center}
    \includegraphics[width=0.7\linewidth]{Figures/marion_beam_huts_2020.pdf}
    %/Users/sievers/hirax/outriggers/marion_beam_huts_2020.pdf
    \caption{Synthesized beam at 5 MHz from the full \albatros\ array.
      We use an octave of bandwidth (3.5 to 7 MHz), and find the
      ensuing synthesized beam has a FWHM of about 7 arcminutes.}
    \label{Fig:beam}
  \end{center}
\end{figure}
